---
title: "Untitled"
author: "Ellie Mainou"
date: "1/23/2023"
output: html_document
---

```{r}
library(readxl)
library(readr)
library(deSolve)
library(cubature)
library(pracma)
library(Bhat)
library(readr)
```


```{r}
DataB2 <- read.csv("TimeToVR/Branching Process/LastUndetFirstDet_B2.csv", header=TRUE)
DataC5 <- read.csv("TimeToVR/Branching Process/LastUndetFirstDet_C5.csv", header=TRUE)
DataC4 <- read.csv("TimeToVR/Branching Process/LastUndetFirstDet_C4.csv", header=TRUE)
```

```{r}
#Setup for parameter values 
namescol<-c("a", "q0", "delay1", "delay2", "delay3")
namesrow<-c("estimate", "95CILow", "95CIHigh")
BestB2Prms<-as.data.frame(matrix(data=NA, nrow=length(namesrow), ncol=length(namescol)))
colnames(BestB2Prms)<-namescol
rownames(BestB2Prms)<-namesrow
#estimates
BestB2Prms$a[1]=0.29
BestB2Prms$q0[1]=0.98
BestB2Prms$delay1[1]=23.5
BestB2Prms$delay2[1]=22.4
BestB2Prms$delay3[1]=9.28
#Low value of the 95% CI
BestB2Prms$a[2]=0.11
BestB2Prms$q0[2]=0.94
BestB2Prms$delay1[2]=23.3
BestB2Prms$delay2[2]=22.1
BestB2Prms$delay3[2]=9.22
#High value of the 95% CI
BestB2Prms$a[3]=0.71
BestB2Prms$q0[3]=1
BestB2Prms$delay1[3]=23.7
BestB2Prms$delay2[3]=23.6
BestB2Prms$delay3[3]=9.34
```


### Antibody therapy

How does the cumulative probability of rebound change if we increase f by 10%, 50% or 90%? 

1. We estimate the curve for the data (f, LR size) for the subject using parameter estimates. 
2. We recreate the same curve, this time with increased f. If the new value of f is greater than 1, then we stop. 
3. We find the median time to VR (day at which PVR=0.5) for each value of f. 
4. Create a summary figure indicating by how much the median time to viral rebound changes



```{r}
#Matrix to store median time to viral rebound for each monkey
MedianTVR<-as.data.frame(matrix(data=NA, nrow=nrow(DataB2), ncol=5)) # NULL 
names<-c("ID", "f", "10%","50%", "90%" )
colnames(MedianTVR)=names
MedianTVR$ID=DataB2$ID

for (n in 1:nrow(DataB2)){
FirstDet <- DataB2$FirstDet[n]
LastUndet <- DataB2$LastUndet[n]
Neut_Percent <- DataB2$Neut_Percent[n]/100
CD4_Data<-DataB2$CD4_Wk0_ul[n]
IPDA_Data<-DataB2$IPDA[n]
Det_IPDA_Data= DataB2$Det_IPDA[n]

CD4_Data<-CD4_Data*1e3*162 #over the entire monkey 

f<-c(Neut_Percent, 1.1*Neut_Percent, 1.5*Neut_Percent, 1.9*Neut_Percent)
for(k in 1:length(f)){
  if (f[k]>=1.00){f[k]=1}
}

f<-f[!duplicated(f)]

CD4<-CD4_Data
IPDA<-IPDA_Data
Det_IPDA<-Det_IPDA_Data
LR<-log10(CD4*IPDA/1e6)


firstdet_alldata <- NULL
lastundet_alldata <- NULL
# model
ts<-seq(0,60,by=1)

pvr<-as.data.frame(matrix(data=NA, nrow=length(ts), ncol=length(f))) # NULL 

for (i in 1:length(f)){
  for (jj in c(1:length(ts))) {
    
      a=BestB2Prms$a[1]
      q0=BestB2Prms$q0[1]
      delay1=BestB2Prms$delay1[1]
      delay2=BestB2Prms$delay2[1]
      delay3=BestB2Prms$delay3[1]
     
      q=min(q0*f[i], 1)
      delay=delay1+delay2*f[i]-delay3*LR
      pvr[jj, i] <- 1 - exp(-LR*a*(1-q)*(ts[jj]-delay))
      if (ts[jj]<=delay) {pvr[jj, i]<-0} # if t<delay, pvr=0 for that monkey
      
  }
     MedianTVR[n, i+1]= min(which(pvr[, i]>=0.5))

}

#Plot results
ID.current <- DataB2$ID[n]
bquote(ID == ID.current)
bquote(ID == .(ID.current))

y<-c("Original", "10%", "50%", "90%")

for (i in 1:length(f)){
plot(ts, pvr[, i], type="l", col=plotcolors[i], xlim=c(0, 60), ylim=c(0, 1), xlab="Time since ATI (days)", ylab="Cum. Prob. Rbd",  main = bquote(ID == .(ID.current)))
grid(nx = NULL, ny = NULL, col = "lightgray", lty = "dotted",
     lwd = par("lwd"), equilogs = TRUE)
par(new=TRUE)
}
legend("topleft", legend=y[1:length(f)], col=plotcolors[1:length(f)], lty=1, cex=0.8 )

}

```

Create summary figure 

```{r}
DiffMedian<--as.data.frame(matrix(data=NA, nrow=nrow(DataB2)*2, ncol=2)) 
colnames(DiffMedian)<-c("Diff", "Increase")
DiffMedian$Increase=c(rep(10, 10), rep(50, 10))
DiffMedian$Diff[1:10]=MedianTVR$`10%`-MedianTVR$f
DiffMedian$Diff[11:20]=MedianTVR$`50%`-MedianTVR$f

boxplot(Diff~Increase,data=DiffMedian, main="Increase in Median time to rebound",
   xlab="% Increase in Neutralization", ylab="Increase in median time to rebound (days)")
```


### Latency reversing agents 

How does the cumulative probability of rebound change if we decrease the latent reservoir by 10%, 50% or 90%? 

1. We estimate the curve for the data (f, LR size) for the subject using parameter estimates. 
2. We recreate the same curve, this time with decreased LR.The way we estimate the decreased LR is by decreasing the IPDA measurement. If the new value of IPDA becomes 0, then we stop. 
3. We find the median time to VR (day at which PVR=0.5) for each value of f. 
4. Create a summary figure indicating by how much the median time to viral rebound changes



```{r}
#Matrix to store median time to viral rebound for each monkey
MedianTVRLR<-as.data.frame(matrix(data=NA, nrow=nrow(DataB2), ncol=5)) # NULL 
names<-c("ID", "LR", "10%","50%", "90%" )
colnames(MedianTVRLR)=names
MedianTVRLR$ID=DataB2$ID

for (n in 1:2){#nrow(DataB2)){
FirstDet <- DataB2$FirstDet[n]
LastUndet <- DataB2$LastUndet[n]
Neut_Percent <- DataB2$Neut_Percent[n]/100
CD4_Data<-DataB2$CD4_Wk0_ul[n]
IPDA_Data<-DataB2$IPDA[n]
Det_IPDA_Data= DataB2$Det_IPDA[n]

CD4_Data<-CD4_Data*1e3*162 #over the entire monkey 

IPDAall<-c(IPDA_Data, 0.9*IPDA_Data, 0.5*IPDA_Data, 0.1*IPDA_Data)

IPDAall<-IPDAall[!duplicated(IPDAall)]

CD4<-CD4_Data
IPDA<-IPDAall
Det_IPDA<-Det_IPDA_Data
LR<-log10(CD4*IPDA/1e6)
f<-Neut_Percent

firstdet_alldata <- NULL
lastundet_alldata <- NULL
# model
ts<-seq(0,60,by=1)

pvr<-as.data.frame(matrix(data=NA, nrow=length(ts), ncol=length(LR))) # NULL 

for (i in 1:length(IPDA)){
  for (jj in c(1:length(ts))) {
    
      a=BestB2Prms$a[1]
      q0=BestB2Prms$q0[1]
      delay1=BestB2Prms$delay1[1]
      delay2=BestB2Prms$delay2[1]
      delay3=BestB2Prms$delay3[1]
     
      q=min(q0*f, 1)
      delay=delay1+delay2*f-delay3*LR[i]
      pvr[jj, i] <- 1 - exp(-LR[i]*a*(1-q)*(ts[jj]-delay))
      if (ts[jj]<=delay) {pvr[jj, i]<-0} # if t<delay, pvr=0 for that monkey
      
  }
     MedianTVRLR[n, i+1]= min(which(pvr[, i]>=0.5))

}

#Plot results
ID.current <- DataB2$ID[n]
bquote(ID == ID.current)
bquote(ID == .(ID.current))

y<-c("Original", "10%", "50%", "90%")

for (i in 1:length(LR)){
plot(ts, pvr[, i], type="l", col=plotcolors[i], xlim=c(0, 60), ylim=c(0, 1), xlab="Time since ATI (days)", ylab="Cum. Prob. Rbd",  main = bquote(ID == .(ID.current)))
grid(nx = NULL, ny = NULL, col = "lightgray", lty = "dotted",
     lwd = par("lwd"), equilogs = TRUE)
par(new=TRUE)
}
legend("topleft", legend=y[1:length(f)], col=plotcolors[1:length(f)], lty=1, cex=0.8 )

}

```